Data Cleaning

### 2024-11-27 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

>>>>

## Attention Checks

```{r}
df <- df |>
  dplyr::mutate(
    A1 = dplyr::case_when(
      Sexual_State_A == 6 | Sexual_State_A == 5 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A2 = dplyr::case_when(
      Anxious_SkinThermo_A == 0 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A3 = dplyr::case_when(
      Nociception_ColonBladder_A == 0 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A4 = dplyr::case_when(
      Sensitivity_Cardiac_A == 6 | Sensitivity_Cardiac_A == 5 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A5 = dplyr::case_when(
      Sensitivity_Gastric_A == 6 | Sensitivity_Gastric_A == 5 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A6 = dplyr::case_when(
      Accuracy_Respiratory_A == 0 | Accuracy_Respiratory_A == 1 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A7 = dplyr::case_when(
      Accuracy_Genital_A == 0 ~ "Pass",
      TRUE ~ "Fail"
    ),
    A8 = dplyr::case_when(
      Confusion_ColonBladder_A == 6 ~ "Pass",
      TRUE ~ "Fail"
    ),
  )

df
```
